\section{Survey of Current Landscape}\label{survey-of-current-landscape}

\textbf{Authorship}

\begin{longtable}[]{@{}llll@{}}
\toprule
Version & Date & Modified by & Summary of changes\tabularnewline
\midrule
\endhead
0.1 & 2017-06-03 & Andres Ardila & Working draft\tabularnewline
0.2 & 2017-07-07 & Andres Ardila & Added section on
Talend\tabularnewline
\bottomrule
\end{longtable}

\begin{verbatim}
//TODO diagram illustrating the pipeline to better describe where each company is positioned
1.
\end{verbatim}

\subsection{OpenSensors.io}\label{opensensors.io}

https://www.opensensors.io

\subsubsection{Features}\label{features}

\begin{quote}
Securely manage your private IoT network {[}\ldots{}{]} whether you are
a startup or an enterprise
\end{quote}

\begin{itemize}
\tightlist
\item
  IoT device management
\item
  Real-time and historical APIs
\item
  Analytics
\item
  Ability to run infrastructure in user's own dedicated cloud network
\item
  Integration with user's backend systems
\item
  Secure data sent to the cloud using TLS
\item
  Set policies on who can sees the data by users or groups of engineers
\item
  Triggers when data hits certain thresholds and alert engineers when
  device is down
\end{itemize}

\paragraph{Hardware agnostic}\label{hardware-agnostic}

Provides support for open protocols, use existing SDKs to quickly get up
and running using MQTT or HTTPS protocols. Their partnership program
includes hardware providers and manufacturing firms.

\subsubsection{Segments}\label{segments}

\begin{itemize}
\tightlist
\item
  \textbf{Workspace planning}: ``Use sensors and our data platform to
  understand if you are using it efficiently and forecast your future
  needs.''
\item
  \textbf{Environment sensing}: Open Data communities to contribute and
  use data from environmental sensors around you. You can get air
  quality data and traffic data for free.
\end{itemize}

\subsubsection{Customers}\label{customers}

\begin{itemize}
\tightlist
\item
  \textbf{Customers} (TODO)
\item
  \textbf{Partners} are hardware manufacturers and design firms (OEMs)
  looking to deliver client projects
\end{itemize}

\subsubsection{Analysis}\label{analysis}

\begin{itemize}
\tightlist
\item
  Not really open. There is no sign-up with which one can get access to
  the allegedly ``open'' data. As a result, one can conclude that their
  focus is the OEM sector as opposed to ``data scientists looking to
  create interesting mash-ups of data.''
\item
  \ldots{}
\end{itemize}

\subsection{PubNub}\label{pubnub}

https://www.pubnub.com/

\subsubsection{Features}\label{features-1}

\paragraph{Scalability}\label{scalability}

15 globally replicated points of presence transacting over 1.5 trillion
messages for 300 million unique devices per month.

\paragraph{Storage}\label{storage}

15 globally replicated points of presence transacting over 1.5 trillion
messages for 300 million unique devices per month.

\subsubsection{Segments}\label{segments-1}

\subsubsection{Customers}\label{customers-1}

\subsubsection{Analysis}\label{analysis-1}

\subsection{Talend}\label{talend}

https://www.talend.com/resource/sensor-data/

Talend is //TODO

\subsubsection{Features}\label{features-2}

\subsubsection{Segments}\label{segments-2}

\subsubsection{Customers}\label{customers-2}

\subsubsection{Analysis}\label{analysis-2}
