\section{Project Management \& Organization}\label{sec:organization}

\textbf{Authorship}

\begin{longtable}[]{@{}llll@{}}
\toprule
Version & Date & Modified by & Summary of changes\tabularnewline
\midrule
\endhead
0.0.1 & 2017-07-19 & Andres, Oliver & Sections and initial
outline\tabularnewline
0.1.0 & 2017-07-27 & Oliver & Outline \& first written
draft\tabularnewline
0.2.0 & 2017-07-28 & Oliver & Rephrased \& extended team
section\tabularnewline
\bottomrule
\end{longtable}

The main challenge of project management is to achieve specific results
within a given scope, time, quality and budget. At the end of every
successful project, stands a unique product meeting the specified
requirements. This chapter elaborates on the available resources and the
development process and chosen approach. The resources that this chapter
will focus on are the heterogeneous team and a limited budget.

\subsection{The Team}\label{the-team}

The project team consisted of seven masters students majoring in
computer science, computer engineering and information systems
management. Moreover, the team members are native of five different
countries with different cultural backgrounds and native languages. Due
to varying English skills and professional experience some discussion
resulted to be time consuming. Furthermore, most members work besides
being students, hence schedules had to be aligned accordingly.

The team was organized into expert groups for the various building
blocks with one person in a coordinative role as the project manager.
Thus, a hierarchy was formed within the group that was hard to enforce
since in the end, the team was formed of peers. In the beginning, two
teams had been formed; one that was responsible for the importing
framework and data sources and one for the database and infrastructure.
Throughout the project period the roles of several members shifted. In
the end, one member focused on the modeling and administration of data
sources, another member focused on the infrastructure provisioning and
deployment, the team responsible for the importing framework consisted
of three persons and lastly, one team two person team worked on the
backend.

\subsection{Constraints}\label{constraints}

Like every other project, this one was subject to several constraints.
The very nature of a project makes it a temporary endeavor. Thus, the
product had to be finished within eleven weeks starting April 27 and
ending July 13. Additionally, towards the end of the first half June 1,
an interim meeting was held. During these eleven weeks three feedback
sessions were held,one of them before the interim meeting and two after.
After July 13 the two more weeks were available to write the
documentation.

Moreover, monetary restrictions added an extra level of difficulty.
While developing software consisting of several disparate building
blocks, it is crucial to deploy and test the components individually and
collectively. Due to lack of an own infrastructure, the only feasible
way to conduct testing - in functionality and performance - was to use a
cloud provider. Owing to no available budget the decision for the US\$100
student grant offered by Amazon Webservices (AWS) was made.
Nevertheless, this added even more effort to receive access to the
student grant and, furthermore, to also be able to use all of the
services provided. Some members did not receive any free credit from
AWS.

Moreover, the budget constraints forced the team to start and terminate
the whole infrastructure every time a test was conducted. In other
words, a significant amount of time was necessary to create the test
environment each time, which put additional strains to compensation of
the already strict time limit. Hence, a significant effort was put into
automating processes in order to provision the infrastructure and
deployment of components.

Having dedicated infrastructure from the beginning would have allowed to
focus more on the actual challenges of the project itself.

\subsection{Development Process \&
Approach}\label{development-process-approach}

To best commence the given challenges and requirements, we decided for
an agile development process. To be more specific, we used a
stripped-down Scrum approach. In this approach, the distinction between
different roles was not strict so that every team member held
simultaneously the role of a product owner and developer for his
specific building block of the global architecture. The same is
applicable for the role of the Scrum Master, which was shared among the
whole team, but still was mainly the responsibility of the Project
Manager. Specifically, this means that every team member was encouraged
to ensure an agile process and administrate issues. Furthermore, the
workflow was adapted to our specific flow of work so that we convened a
sprint meeting weekly with an additional weekly interim meeting and
omitted the daily scrum.

To keep track of every issue and the global progress, we used a Trello.
Trello follows the Kanban model and arranges issues into lists. We
created four lists to mirror the lifecycle of issues. The first list -
product backlog - is where requirements,issues and generally tasks are
created that the product must satisfy. This list was populated
continously as the project progressed. The next list included tasks due
until the next sprint meeting. Following the next list contained tasks
that were currently worked on and finally, all finished tasks were
archived.

Slack was the chosen medium of communication, because it allows to
distinguish between independent topics by using channels. Additionally,
a shared calendar was used to remember deadlines and a shared file
system to store the protocols of our meetings. More importantly we used
GitHub to store the code written. We formed an organization and create a
separate repository for every component.

In order to integrate the tools we used as well as to automate
workflows a service called Zapier was used. We used it to receive
notifications about changes on GitHub and Google Drive and the progress
made on Trello. Though, after the trial ended the functionality was
limited so that only notifications about GitHub updates were send.
